Comparison to other studies

### 2024-11-06 pages/framework.qmd
docs(reflections+framework): add toms comments from shared hackmd file
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

@@

## Contents of the framework

@@

>>>>

<!--TODO: Divide this into STARS framework and STRESS framework reflections-->

@@

<!--TODO: Make a paper with STRESS specific reflections - so ensure these are incorporated in others, then have discussion page where I walk through STRESS and, based on what I have found, suggest what was helpful in framework, what was missing, and so on.

* Consider: which of my reflections pertain to what is in the article, v.s. what is in the repository - e.g. the scenarios being used is important in both - but mine is actually referring more to the repository, hence relevant to STARS more-so than STARS-->

## Contents of the STARS framework

@@

* Tom: Agree this is a good idea

### 2024-11-06 pages/other_studies.qmd
chore(docs): correct licence spelling
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

@@

    * make all code and data available with an appropriate license

>>>>

TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting

@@

    * make all code and data available with an appropriate licence
